A standardized framework for risk-based assessment of treatment effect heterogeneity in observational healthcare databases

### 2021-08-25 submission/manuscript.rmd
responding to reviewer 1

@@

@@

< < ADD > >

@@

< < ADD > >

@@

< < EDIT > >

@@

< < EDIT > >

< < OLD > >

@@

< < OLD > >

@@

@@

@@

< < MOVE > >

>>>>

\> > EDIT > >

***In recent years, a large number of methods has been developed for the
assessment of HTE, mainly in the RCT setting. Earlier work suggested separating
HTE analyses into exploratory, confirmatory, descriptive and predictive
[@Varadhan2013]. Exploratory analyses focus on hypothesis generation,
confirmatory analyses test subgroup effect hypotheses, descriptive analyses aim
at facilitating future synthesis of subgroup effects and predictive analyses
predict probabilities of benefit or harm in individual patients. Predictive HTE
approaches can be further subdivided into risk modeling, treatment effect
modeling and optimal treatment regime methods, based on the reference class used
for defining patient similarity when making individualized predictions or
recommendations [@Rekkas2020]. We focus on “risk modeling” approaches where
patients are divided into risk strata using either an existing or an internally
developed risk prediction model. Risk-stratum-specific estimates provide an
overview of the evolution of treatment effects with increasing risk both on the
relative and the absolute scale. Recently, systematic guidance on the
application of such methods has been developed [@Kent2010; @Kent2018].***

< < EDIT < <

\> > OLD > >

@@

< < OLD < <

@@

\> > ADD > >

@@

< < ADD < <

@@

\> > EDIT > >

@@

< < EDIT < <

\> > OLD > >

@@

< < OLD < <

@@

## Step 5: Evaluation and presentation of results

@@

\> > MOVE: ps_matching > >

@@

< < MOVE < <
